Dependent Object Types

### 2012-06-30 doc/semester/report.tex
path equality

>>>>

We need to be able to relate path-dependent types after reduction. The
original DOT calculus doesn't have any rules for dealing with
path-equality. Here is an example which motivates the need for
path-equality provisions.

\begin{align*}
&\mlnew b {\Top \mlrefine z {&&\Ldecl X \Top \Top&\\
&&&\ \ldecl l {z.X}&}\ldefs{l = b}}{
\mlnew a {\Top \mlrefine z {\ldecl i {\Top \mlrefine z {&&&\\
&&&\Ldecl X \Bot \Top\\
&&&\ldecl l {z.X}}}&}\ldefs{i = b}}}{
\app {(\abs x \Top x)} {(\app {(\abs x {a.i.X} x)} {a.i.l})}}
\end{align*}

$a.i.l$ reduces to $b.l$. $b.l$ has type $b.X$, so we need $b.X <:
a.i.X$. This cannot be established with the current rules: it is not
true in general, but true here because $a.i$ reduces to $b$. Hence,
the need for acknowledging path equality.
